On Cores of Ideals with Empty Variety

### 2016-05-12 unsat/paper/irina.tex
Finalize UNSAT core staff(hopefully)

%%This is a very basic article template.
%%There is just one section and two subsections.
\documentclass{article}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\theoremstyle{plain}
\newtheorem{defn}{Definition}[section]
%\usepackage{datetime}
\newtheorem{thm}[defn]{Theorem} % definition numbers are dependent on
% theorem
% %
\newtheorem{prop}[defn]{Proposition} % definition numbers are dependent on
\newtheorem{dem}[defn]{Proof} % definition numbers are dependent on
              % numbers
\newtheorem{exemp}{Example}[defn]
\newtheorem{lema}{\bf Lemma}[defn]

\def\opn#1#2{\def#1{\operatorname{#2}}} % to make operators

\opn\Ker{Ker} \opn\Coker{Coker}  \opn\Hom{Hom} \opn\Im{Im}
\opn\End{End} \opn\Aut{Aut} \opn\defect{def} \opn\ord{ord}
\opn\id{id} \opn\dim{dim} \opn\det{det} \opn\tr{tr} \opn\grad{grad} \opn\lcm{lcm}
\opn\min{min} \opn\max{max} \opn\det{det}
%\def\Frob{{\mathcal F}}
\opn\Span{Span}   \opn\rang{rang}  \opn\id{id} \opn\dim{dim} \opn\ad{ad} \opn\tr{tr} \opn\ker{ker}
\opn\GL{GL} \opn\SL{SL} \opn\mod{mod} \opn\diag{diag}
\opn\min{min} \opn\sgn{sgn} \opn\ini{in_<}  \opn\Mon{Mon} \opn\LC{LC_<}
\opn\LT{LT_<}
\opn\s{supp}

\title{On Cores of Ideals with Empty Variety}

\begin{document}

\maketitle

@@

\end{exemp}				
\begin{thebibliography}{99}

\bibitem{HH}  J\"urgen Herzog, Viviana Ene, \emph{Gr\"obner Bases in Commutative Algebra}, American Mathematical Society, 2012.
\end{thebibliography}

\end{document}

>>>>

\section{Introduction}

{\bf This is the dummy submission uploaded on Feb 21. The final paper will be uploaded on Feb 24, 2016.}

@@

\end{exemp}
